% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base
\begin{thebibliography}{9} 
	\bibitem{web:SIPLIB1}
	S. Ahmed, R. Garcia, N. Kong, L. Ntaimo, G. Parija, F. Qiu, S. Sen. SIPLIB: A Stochastic Integer Programming Test Problem Library. http://www.isye.gatech.edu/~sahmed/siplib, 2015.
	\bibitem{web:SPS}
	SPS: Stochastic Programming Society (https://stoprog.org/what-stochastic-programming).
	\bibitem{book:BL2011}
	Introduction to Stochastic Programming, J. R. Birge, F. Louveaus.
	\bibitem{journal:AG2004}
	S. Ahmed and R. Garcia. "Dynamic Capacity Acquisition and Assignment under Uncertainty," Annals of Operations Research, vol.124, pp. 267-283, 2003.
	\bibitem{journal:KZ2015}
	Kibaek Kim and Victor M. Zavala. "Algorithmic Innovations and Software for the Dual Decomposition Method applied to Stochastic Mixed-Integer Programs" Mathematical Programming Computation, 2015.
	\bibitem{journal:WWH2012}
	J.-P. Watson, D. L. Woodruff, and W. E. Hart, PySP: modeling and solving stochastic programs in Python, Mathematical Programming Computation, 2012.
	\bibitem{web:SMI}
	SMI - Stochastic Modeling Interface. https://github.com/coin-or/Smi
	\bibitem{journal:BEKS2017}
	Julia: A Fresh Approach to Numerical Computing. Jeff Bezanson, Alan Edelman, Stefan Karpinski and Viral B. Shah (2017) SIAM Review, 59: 65–98.
	\bibitem{web:JuMP}
	JuMP - Julia for Mathematical Optimization, https://jump.readthedocs.io/en/latest/index.html
	\bibitem{web:StructJuMP}
	StructJuMP - Parallel algebraic modeling framework for block structured optimization models in Julia, https://github.com/StructJuMP/StructJuMP.jl
	\bibitem{journal:MPT2014}
	F. Maggioni, G. Perboli, and R. Tadei, The multi-path traveling salesman problem with stochastic travel socts: Building realistic instances for city ligistics applications, Transportation Research Procedia, 2014
	\bibitem{journal:PGM2017}
	G. Perboli, L. Gobbato, and F. Maggioni, A progressive hedging method for the multi-path travelling salesman problem with stochastic travel times, IMA Journal of Management Mathematics, 2017
	\bibitem{journal:TPP2017}
	R. Tadei, G. Perboli, and F. Perfetti, The multi-path traveling salesman problem with stochastic travel costs, EURO Journal on Transportation and Logistics, 2017
	\bibitem{journal:LSD1990}
	Andre Langevin, Francois Soumis, and Jacques Desrosiers, Classification of travelling salesman problem formulations, Operations Research Letters, 1990
	\bibitem{journal:JSW1999}
	Soheila Jorjani, Carlton H. Scott, and David L. Woodruff, Selection of an optimal subset of sizes, International Journal of Production Research, 1999	
	\bibitem{journal:GG1978}
	B. Gavish and S.C. Graves, The travelling salesman problem and related problems, Working paper GR-078-78, Operations Research Center, Massachusetts Institute of Technology, 1978
	\bibitem{journal:AAD2014}
	Gustavo Angulo, Shabbir Ahmed, and Santanu S. Dey, Improving the integer L-shaped method, 2014.
	\bibitem{journal:PO2013}
	Anthony Papavasiliou and Shmuel S. Oren, Multiarea stochastic unit commitment for high wind penetration in a transmission constrained network, Operations Research, 2013
	\bibitem{journal:KYZC2017}
	Kibaek Kim, Fan Yang, Victor M. Zavala, and Andrew A. Chien, Data centers as dispatchable loads to harness stranded power, IEEE Transactions on sustainable energy, 2017
	\bibitem{journal:NS2005}
	Lewis Ntaimo and Suvrajeet Sen, The million-variable ``March'' for stochastic combinatorial optimization, Journal of Global Optimization, 2005
	\bibitem{MIPLIB}
	Koch et al., MIPLIB 2010, Mathmatical Programming Computation, 2011
	\bibitem{journal:LLMS2014}
	Lee, C., Liu, C., Mehrotra, S., Shahidehpour, M, MOdeling transmission line constraints in two-stage robust unit commitment problem, IEEE Transactions on Power Systems, 2014
\end{thebibliography}